CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-10 paper/ms.tex
better plot

\includegraphics[width=170mm]{figure_1.png}
 \centerline{Fig.1 The optimized spectrum and the data spectrum}
\bigskip

\includegraphics[width=170mm]{figure_2.png}
 \centerline{Fig.2 The inferred spectrum and the data spectrum}

@@

\centerline{Fig.3 a,b,c vs Mean Fiber Number}
\bigskip

@@

\centerline{Fig.4 Delta-chi-squared vs Mean Fiber Number}
\bigskip

@@

@@

\centerline{Fig.5 Spectrum of the four stars with biggest delta-chi-squared. }

\centerline{Fig.6 Spectrum of the four stars with smallest delta-chi-squared. }

@@

\centerline{Fig.7 Spectrum of the four stars with b closest to 1. }

@@

\centerline{Fig.8 Spectrum of the four stars with biggest a+c-b. }

@@

\centerline{Fig.9 Spectrum of the four stars with biggest $a-c$.}

@@

\centerline{Fig.10 Spectrum of the four stars with biggest $c-a$.}

@@

\includegraphics[width=170mm]{figure_11.png}
\bigskip

\centerline{Fig.11 $Teff$ vs $log g$}
\bigskip

>>>>

\includegraphics[width=170mm]{figure_1.png}
 \centerline{Fig.1 The spectrum of Star A, B, C and D}

@@

\includegraphics[width=170mm]{figure_2.png}
\bigskip

\centerline{Fig.2 a,b,c vs Mean Fiber Number}
\bigskip

@@

\centerline{Fig.3 Delta-chi-squared vs Mean Fiber Number}
\bigskip

@@

\centerline{Fig.4 Spectrum of the four stars with biggest delta-chi-squared. }

@@

\centerline{Fig.5 Spectrum of the four stars with smallest delta-chi-squared. }

@@

\centerline{Fig.6 Spectrum of the four stars with b closest to 1. }

@@

\centerline{Fig.7 Spectrum of the four stars with biggest a+c-b. }

@@

\centerline{Fig.8 Spectrum of the four stars with biggest $a-c$.}

@@

\centerline{Fig.9 Spectrum of the four stars with biggest $c-a$.}

@@

\centerline{Fig.10 $Teff$ vs $log g$}
\bigskip
